Fast Random Integer Generation in an Interval

### 2024-02-06 Presentation/preliminaries.tex
color in math mode + OpenBSD

@@

    \begin{exampleblock}{}<+->
        \begin{center}
            $\texttt{rand()} \Mod n$
        \end{center}
    \end{exampleblock}

@@

\iffalse
\begin{frame}{The Naive Approach}
    \begin{alertblock}{Is the generated number uniform in $\boldsymbol{[0,n)}$?}<+->
        \onslide<+->{Consider the case where $W = 4$ and $n = 3$.}
        \onslide<+->{Then, $[0,2^W)$ is}
        \onslide<+->{\begin{align*}
            0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15
        \end{align*}}
        \onslide<+->{Apply $\left(x \Mod 3\right)$ for every $x$ and get}
        \onslide<+->{\begin{align*}
            0,1,2,0,1,2,0,1,2,0,1,2,0,1,2,0
        \end{align*}}
        \onslide<+->{\GB{$0$} appears \ER{$6$} times, \GB{$1$} appears \ER{$5$} times, and \GB{$2$} appears \ER{$5$} times!}
    \end{alertblock}

\end{frame}
\fi

\begin{frame}{The Naive Approach}
    \pause 
    \onslide<+->{In general, applying $\left(x \Mod n\right)$ to $[0,2^W)$ yields}
    \onslide<+->{\begin{align*}
        \overbrace{\underbrace{\overbrace{0,1,\ldots,n - 1}^{\text{$n$ values}},\overbrace{0,1,\ldots,n - 1}^{\text{$n$ values}},\ldots,\overbrace{0,1,\ldots,n - 1}^{\text{$n$ values}}}_{\text{$\left(2^W \div n\right) \cdot n$ values}},\ER{\underbrace{0,1,\ldots,\left(2^W \Mod n\right) - 1}_{\text{$2^W \Mod n$ values}}}}^{\text{$2^W$ values}}
    \end{align*}}

@@

    \onslide<+->{\GB{Every} approach that maps every integer in $[0,2^W)$ to a single number in $[0,n)$}
    \onslide<+->{does \ER{not} generate uniform random integers in one step.}

>>>>

    \begin{definition}[Power Remainder]<+->
        For $W,n \in \mathbb{N}$, we write $\RNW$ for $2^W \Mod n$.
    \end{definition}

@@

    \onslide<+->{\begin{center}
            $\texttt{rand()} \Mod n$
    \end{center}}

@@

\begin{frame}{The Naive Approach}
    \pause 
    \onslide<+->{In general, applying $x \Mod n$ to $[0,2^W)$ yields}
    \onslide<+->{\begin{align*}\everymath{} % Allows specific coloring
        \overbrace{\underbrace{\overbrace{0,1,\ldots,n - 1}^{\text{$n$ values}},\overbrace{0,1,\ldots,n - 1}^{\text{$n$ values}},\ldots,\overbrace{0,1,\ldots,n - 1}^{\text{$n$ values}}}_{\text{$\left(2^W \div n\right) \cdot n$ values}},\ER{\underbrace{0,1,\ldots,\RNW - 1}_{\text{$\RNW$ values}}}}^{\text{$2^W$ values}}
    \end{align*}}

@@

    \onslide<+->{\GB{Every} approach that maps every integer in $[0,2^W)$ to a single number in $[0,n)$}
    \onslide<+->{does \ER{not} generate uniform random integers in one step}
    \onslide<+->{whenever $n$ does not divide $2^W$.}

    \onslide<+->{\GB{Idea:} Use \ER{rejection sampling} to achieve uniformity!}
\end{frame}
